\begin{thebibliography}{100} % 100 is a random guess of the total number of
    %references
    
    \bibitem{1} Shannon, C.E.,
    			"Prediction and Entropy of Printed English",
			\emph{Bell System Technical Journal}, Vol. 30, Issue 1., pp. 50-64
			January 1951
    
    \bibitem{2}Escandell-Vidal, V., Marrero, V., and Perez, P.,
    			"Prosody, information structure and evaluation",
			\emph{https://www.researchgate.net/publication/291037643\_Prosody\_ \\
			information\_structure\_and\_evaluation} January 2014

    \bibitem{3} Shannon, C.E.,
    			"A Mathematical Theory of Communication",
			\emph{The Bell System Technical Journal},
			Vol. 27, pp. 379 - 423, July 1948,
			Reprinted 623-656, October 1948

    
    \bibitem{4} Demol, M., Verhelst, W., and Verhoeve, P.,     
    			"The Duration of Speech Pauses in a Multilingual Environment",
			\emph{INTERSPEECH 2007}, 
			January 2007
    
    \bibitem{5} Demol, M., Verhelst, W., and Verhoeve, P.,
    			"A Study of Speech Pauses for Multilingual Time-Scaling Applications", 
			\emph{https://www.researchgate.net/publication/
			228740134\_A\_Study\_of\_Speech\_Pauses\_for\_Multilingual\_Time-Scaling\_Applications}

    
    \bibitem{6}	Islam, M.M., and Sultana, N.,
    			"Comparative Study of Classification Algorithms used in Sentiment Analysis",
			\emph{International Journal of Computer Applications},
			Vol. 182., pp. 1-7, October 2018

    
    \bibitem{7}Back, A.D., Angus, D., and Wiles, J., "Fast Entropy Estimation for Natural Sequences
    			\emph{https://arxiv.org/abs/1805.06630}, May 2018
    
    
    \bibitem{8} Watson, C.M., Chenery, H. J., and Carter, M.S.,
    			"An analysis of trouble and repair in the natural conversations of people with dementia of the Alzheimer’s type",
			\emph{Aphasiology} Vol. 13, Issue. 3, August 2010

    
    \bibitem{9} A.Batliner, K.Fischer, R.Huber, J.Spilker, and E.Nöth,
    			"How To Find Trouble In Communication",
			\emph{Speech Communication},
			Vol. 40, Issue 1-2, Pages 117-143, April 2003 
			 
    
    \bibitem{10} Verma, M.H., 
    			"Communication Breakdown : A Pragmatics Problem",
			\emph{The Criterion: An International Journal in English},
			Issue 12, February 2013.

    
    \bibitem{11} Abadi, M., Agarwal, A., Barham, P., Eugene Brevdo., et. al.,
    			"TensorFlow: Large-Scale Machine Learning on Heterogeneous Systems",
			\emph{http://tensorflow.org/}, 2015

    
    \bibitem{12} Madan, A., and Gupta, D.,
    			"Speech Feature Extraction and Classification: A Comparative Review",
			\emph{Madan2014SpeechFE}, 2014

    
    \bibitem{13}Deng, L., and Li, X., 
    			"Machine Learning Paradigms for Speech Recognition: An Overview",
			\emph{IEEE TRANSACTIONS ON AUDIO, SPEECH, AND LANGUAGE PROCESSING},
			Vol.21, pp. 1060-1089, 5 May 2013

    
    \bibitem{14} Eyben, F.,
    			"Real-time Speech and Music Classification by Large Audio Feature Space Extraction",
			\emph{2190-5053}, DOI: 10.1007/978-3-319-27299-3

    
    \bibitem{15} Manex, S., Perez, S., Torres, M.I., and Pozo, A.D.,
    			"Entropy-Driven Dialog for Topic Classification: Detecting and Tackling Uncertainty"
			\emph{Dialogues with Social Robots},
			Vol. 427, pp. 171-182., 25 December 2016
    
    \bibitem{16} Gianvecchio, S., Xie, M., Wu, Z., and Wang, H.,
    			"Measurement and Classification of Humans and Bots in Internet Chat"
			\emph{IEEE/ACM Transactions on Networking},
			Vol. 19., Issue. 5., pp. 1557 - 1571, October 2011
    
    \bibitem{17} Telesca, L., and Lovallo, M., 
    			"On the performance of Fisher Information Measure and Shannon entropy estimators",
			\emph{Physica A: Statistical Mechanics and its Applications},
			Vol. 484, pp. 569 - 576, 15 October 2017

    
    \bibitem{18} Mishra, A.R., Jain, D., Hooda, D. S.,
    			"Exponential Intuitionistic Fuzzy Information Measure with Assessment of Service Quality",
    			\emph{International Journal of Fuzzy Systems},
			Vol. 19, Issue 3., pp. 788-798., June 2017

    
    \bibitem{19} Tongal, H., and Sivakumar, B.,
    			"Cross-entropy clustering framework for catchment classification",
			\emph{Journal of Hydrology}, Vol. 552, pp.433-446, July 2017

    \bibitem{20}Zhu, Z., Novikova, J., and Rudzicz, F.,
    			"Isolating effects of age with fair representation learning when assessing dementia",
    			\emph{https://arxiv.org/abs/1807.07217},
			July 2018

    
    \bibitem{21}Zhu, Z., Novikova, J., and Rudzicz, F.,
    			"Detecting cognitive impairments by agreeing on interpretations of linguistic features",
			\emph{https://arxiv.org/abs/1808.06570}, August 2018
    
    \bibitem{22} Demol, M., Verhelst, W., and Verhoeve, P.,     
    			"The Duration of Speech Pauses in a Multilingual Environment",
			\emph{INTERSPEECH 2007}, 
			January 2007

    
    \bibitem{23} Yu, Y., Vrbik, P., 
    			"Calpy" 
			\emph{https://github.com/YvonneYYu/calpy}, June 2019

    \bibitem{24} Shigemitsa, Y., 
    			"Different Interpretations of Pauses in Natural Conversation ---Japanese, Chinese and Americans 1",
			\emph{https://www.researchgate.net/publication/264877163\_Different\_ \\ 
			Interpretations\_of\_Pauses\_in\_Natural\_Conversation\_---Japanese\_Chinese\_and\_Americans\_1}

    \bibitem{25} Campione, E., and Véronis, J., 
    			"A Large-Scale Multilingual Study of Silent Pause Duration by Campione and Veronis",
			\emph{ISCA Archive}, April 2002
    

 
\end{thebibliography}

%\section{Bibliography}

